---
title: "Regression Analysis Webpage"
author: "W.C. NG"
date: "26 June 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(shiny)
```

## Overview

Regression analysis is a statistical tool which is used to investigate the relationship between the predictor and repsonse. This webpage shows how one can use this tool to understand the data better and to perform statistical prediction using linear regression analysis. 

## Case Study

We use mtcars dataset for this case study. A summary of data is shown at below. 
```{r, comment=''}
head(mtcars)
```
In the next slide we shows the regression analysis webpage. 

## Regression Analysis: Demo

```{r}

sidebarPanel(
    # Select Response
    selectInput(inputId = "res", 
                label = "Select Response (Y-axis):", 
                choices = names(mtcars)),
    # Select Predictor
    selectInput(inputId = "pred", 
                label = "Select Predictor (X-axis):", 
                choices = names(mtcars)),
    # Check if lm required
    checkboxInput(inputId = 'lm', 
                  label = 'Show linear regression?', 
                  value = TRUE))

mainPanel(renderPlot({
  
        gg <- ggplot(mtcars, aes_string(x = input$pred, y = input$res)) + 
            geom_point() +  
            xlab("Predictor") +
            ylab("Response") +
            theme(legend.title = element_blank(),
                  axis.title.x = element_text(face="bold", size=15),
                  axis.text.x  = element_text(vjust=0.5, size=15),
                  axis.title.y = element_text(face="bold", size=15),
                  axis.text.y  = element_text(vjust=0.5, size=15))  
        if (input$lm == TRUE){ gg <- gg + geom_smooth(method = 'lm')}
        gg }))
```

## Thank you!
### To access the application on web: https://wc-ng.shinyapps.io/Regression_Analysis/
### To access the source code: https://github.com/wengchiat/dp-cp

